Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-03-08 Master Thesis/synopsis.tex
Update theorem on henselizations

\begin{theorem}\label{theorem-henselization}
Let $K$ be a field and $v\in\operatorname{Spv}(K)$. Then there is a Galois extension $K_v/K$ with a henselian extension $\overline{v}$ of $v$ with the following characterization:

@@

Furthermore, $\overline{v}$ has the same value group as $v$ and $k(\overline{v}) = k(v)$. $G_{K_v}$ is the decomposition group $G_{\overline{v}}\subset G_K$ of the unique extension of $\overline{v}$ to $K^\text{s}$. $K_v$ is called a \textit{henselization} of $K$ with respect to $v$. Any two henselization of $K$ with respect to $v$ are $K$-conjugate.
\end{theorem}

@@

The second assertion follows from the first one, applied to $L$, by using the following equation of supernatural numbers ([E], Theorem 20.21):
\[ [L:K] = (\Gamma':\Gamma) \cdot [k':k]\cdot p^d \]
for some $d \leq \infty$, where $\Gamma'$ denotes the value group and $k'$ the residue field of the unique prolongation of $w$ to $L$. Note that $\operatorname{rank}(w) = \operatorname{rank}(v)$ in an algebraic field extension ([ZS], Ch. VI, §11, Lemma 1 and 2).
\end{proof}

>>>>

\begin{theorem}\label{theorem-henselization}
Let $K$ be a field and $v\in\operatorname{Spv}(K)$. Then there is a separable extension $K_v/K$ with a henselian extension $\overline{v}$ of $v$ with the following characterization:

@@

$K_v$ is called a \textit{henselization} of $K$ with respect to $v$. Furthermore, $\overline{v}$ has the same value group as $v$ and the same residue field $k(\overline{v}) = k(v)$. $G_{K_v}$ is the decomposition group $G_{\overline{v}}\subset G_K$ of the unique extension of $\overline{v}$ to $K^\text{s}$.

Conversely, taking the fixed field of the decomposition group of an extension $\overline{v}'$ of $v$ in $K^\text{s}$ yields a henselization of $K$ with respect to $v$. Any two of such henselizations are $K$-conjugate.
\end{theorem}

@@

The second assertion follows from the first one, applied to $L$, by using the following equation of supernatural numbers ([E], Theorem 20.21):
\[ [L:K] = (\Gamma':\Gamma) \cdot [k':k]\cdot p^d \]
for some $d \leq \infty$, where $\Gamma'$ denotes the value group and $k'$ the residue field of the unique prolongation of $w$ to $L$. Note that $\operatorname{rank}(w) = \operatorname{rank}(v)$ in an algebraic field extension ([ZS], Ch. VI, §11, Lemma 2).
\end{proof}
